A Fully Decentralized Infrastructure for Subscription-based IoT Data Trading

### 2020-11-12 paper.tex
Use ncku email
Change TA to Accel

\section{Conclusion and Future Work}
\label{section:conclusion}
This paper aims to propose a highly decentralized, autonomous publish/subscribe model that combines data storage and trading together in order to ensure the digital rights of both data providers and consumers during the dynamic data streaming trading. To clarify the data ownership and identity verification, the data stream is stored on the Tangle, transmitted through MAM, and automated by Ethereum smart contracts in our design. Compared to previous works, we (1) identify a trustless data trading infrastructure, (2) ensure the confidentiality of scalable IoT-based sensor data, and (3) consolidate the economic incentives in the entire ecosystem. Meanwhile, we consider the heavy workload of the low-level sensors, conduct an experiment which authenticates the data providers to delegate the MAM operations to TAs, and conclude that the performance of the E2EE approach is more fitting than the MAM solution. In particular, this work discusses the refund mechanism for subscription-based IoT data trading: Launching, voting, and implementing the refunding procedure.

>>>>

\section{Conclusion and Future Work}
\label{section:conclusion}
This paper aims to propose a highly decentralized, autonomous publish/subscribe model that combines data storage and trading together in order to ensure the digital rights of both data providers and consumers during the dynamic data streaming trading. To clarify the data ownership and identity verification, the data stream is stored on the Tangle, transmitted through MAM, and automated by Ethereum smart contracts in our design. Compared to previous works, we (1) identify a trustless data trading infrastructure, (2) ensure the confidentiality of scalable IoT-based sensor data, and (3) consolidate the economic incentives in the entire ecosystem. Meanwhile, we consider the heavy workload of the low-level sensors, conduct an experiment which authenticates the data providers to delegate the MAM operations to Accels, and conclude that the performance of the E2EE approach is more fitting than the MAM solution. In particular, this work discusses the refund mechanism for subscription-based IoT data trading: Launching, voting, and implementing the refunding procedure.
